\chapter{Vertical Head Service Manual}

\section*{Accessories No. 201, resp. 201A}

\begin{tabular}{ll}
    Internal Taper                               & ISO 30              \\
    Spindle Bore                                 & Ø 15 mm             \\
    Diameter of cutter arbors, long and short    & 13-16-22-25,4-27 mm \\
    Inclination                                  & \(360^\circ\)       \\
    Spindle Speeds (by infinitely-variable gear) & 58 - 2000 rpm       \\
\end{tabular}

\section*{Cleaning, Lubrication, and Maintenance}

Upon receipt and during operation, the general guidelines provided for the machine must be observed.
The vertical head includes 3 oilers for pressure lubrication using the pump supplied with the machine.

\section*{Installation}

The vertical head is centered and secured by the two support arms 7.
For installation, insert the gear stud 141 (supplied with the vertical head) into the spindle nose,
then tighten it using the tightening key. Extend one of the support arms 7 by approximately 250 mm and lock the front screw 5.
Mount the vertical head on the cleared arm, unlock screw 5, and insert the second support arm into the corresponding bore of the vertical head.

This mounting process avoids potential jams during simultaneous engagement of both support arms.
Then, press the vertical head against the spindle head, taking care not to damage the gear teeth.
Secure the support arms 7 with the two screws 5 and tighten screw 142, pressing the vertical head firmly against the spindle head to prevent any torsion.
Finally, lock the two fastening screws that hold the vertical head against the spindle head.

\section*{Spindle Cutter Adjustment}

The bearing adjustment is done during the setup of each vertical head, so a new adjustment is necessary only after a relatively long running time.

The front bearing includes a tapered roller bearing 143 from Precision Industrielle in Rueil-Malmaison (France) No. 101.040 / 101.080 (precision 2 Microns).

The rear bearing includes a tapered roller bearing 144 No. 102.035 / 102.072, of the same origin and precision as the front bearing.

\section*{Compensation of Spindle Axial Play}

\begin{enumerate}
    \item Separate the tiltable part from the fixed part by unscrewing the 4 locking nuts.
    \item Unscrew screw 145 and remove cover 147.
    \item Unscrew nut 148 connected to the spindle 149 by the lock washer 150, lifting one of the tabs engaged in one of the nut entries. Remove baffle 146.
    \item Carefully tap the spindle 149 with a lead hammer.
    \item Plane spacer 152 for half of the play to be compensated, which has been previously determined by precise control.
    \item Plane spacer 153 for half of the play to be compensated.
    \item Reassemble the spindle 149 in the reverse direction of disassembly, remembering to fold down the tab of the washer 150 blocking nut 148 and to lock screw 145.
\end{enumerate}
