\chapter{Control and Selection of the Spindle Speeds}
\section*{Spindle Speeds}

Speeds ranging from 56 to 2100 r.p.m., infinitely variable within
these limits, are obtained by means of a belt-type speed-change
gear. The drive is transmitted from the motor to the speed
regulator and the gearbox by means of 2 vee-belts answering to
the following specification:

\begin{itemize}
    \item Brand: Dayton,
    \item Profile: 1 1/\(32"\) x 11/32"
    \item Angle: \(30^\circ\)
    \item Mean length: 48"
\end{itemize}

For instructions as to adjustment of variator, see page \pageref{chap:spindle_speed_variator}.

\section*{Selection of Speeds}

The speed of the belt-type speed-change gear is varied by means
of the handwheel 28, which is locked by means of the knob 29.
The change over from low to high speed is effected by the lever 30.

Handwheel 28 must be operated with the motor running, whereas
\ul{lever 30 must be operated only when the machine is at a standstill.}

If, for instance, a spindle speed of 180 r.p.m. is desired,
handwheel 28 must be turned until the figure 180 appears opposite
the pointer 31. The colours on the spindle-speed scale tally with
the colours marking the positions of the lever 30 (for 180 r.p.m.,
green).

Lever 15, operated in conjuction with a switch, enables the
spindle to be run in either direction (see page \pageref{chap:structural_characteristics_and_handling}, "Starting up").

\section*{Vertical Slide}
\subsection*{Hand Feed}
Hand feed is controlled by means of the handwheel 32.
The vertical feed-spindle has a pitch of 4 mm. and the scale
is graduated in 2/100 mm.; it can be set at zero.

\subsection*{Locking the Vertical Slide}

The vertical slide is locked by means of lever 33.

\section*{Longitudinal Slide}
\subsection*{Hand Feed}

Longitudinal hand feed is controlled by handwheel 34.
The longitudinal spindle has a pitch of 4 mm. and the scale is
graduated in 2/100 mm.; it can be set at zero.

\subsection*{Locking the Longitudinal Slide}

The longitudinal slide is locked by means of lever 35.
ADJUSTING THE TAPER STRIPS of the vertical and longitudinal
slides and spindle head; see page 24.
