\newpage
\section*{Cleaning, Lubrication, and Maintenance}

Upon receipt and during use, the general instructions provided for the machine must be followed.
Do not lift this accessory by its plate but by its base.

\subsection*{Oil Bath}
The worm screw is lubricated by an oil bath.
The filling is done as follows with an oil viscosity of \(3^\circ \mathrm{E}\) at \(50^\circ \mathrm{C}\):
\begin{enumerate}[label=\arabic*.]
    \item Unscrew the plug 96 and fill up to the middle of the level indicator 97.
    \item Once a year, drain and renew the oil after rinsing with petroleum.
\end{enumerate}
The plate also includes 2 oilers for pressure lubrication using the pump supplied with the machine.

\subsection*{Disassembly of the Vernier}
\begin{enumerate}[label=\arabic*.]
    \item Unscrew the screw 98.
    \item Remove the handle 99, the socket 100 carrying the vernier 101, and its spring 102.
\end{enumerate}

\subsection*{Disassembly of the Hole Discs}
\begin{enumerate}[label=\arabic*.]
    \item Unscrew the nut 103 and remove the washer 104.
    \item Remove the handle 105 carrying the piston 106 and the socket 107.
    \item Remove the needles 108 and 109.
    \item Unscrew the 3 screws 110 and remove the disc 111.
\end{enumerate}

\subsection*{Axial Clearance Adjustment of the Worm Screw}
If the axial clearance comes from the teeth:
\begin{enumerate}[label=\arabic*.]
    \item Unscrew the screw 112 completely.
    \item Unscrew the screw 113 according to the importance of the clearance to be adjusted.
    \item Put back the screw 112 and tighten it firmly.
\end{enumerate}

If the axial clearance comes from the axis of the worm screw:
\begin{enumerate}[label=\arabic*.]
    \item Unscrew the screw 94 and remove the eccentric sleeve 95.
    \item Unlock the screw 114 and screw the nut 115 according to the importance of the clearance to be adjusted.
    \item Lock the screw 114.
\end{enumerate}

Only an experienced person should be authorized to carry out this adjustment, which requires the greatest care.
