\chapter{Service Instructions for the High Speed Head \\
SCHAUBLIN 13 \small{Accessory No. 1100}}

\section*{Main Features}
\begin{tabular}{@{}ll@{}}
    Inner spindle cone for E20 collet & E20            \\
    Spindle stroke                    & 60 mm          \\
    Spindle speed (3 x normal speeds) & 170 - 6400 rpm \\
    Spindle tilt                      & 360°           \\
\end{tabular}

\section*{Accessories}
\begin{tabular}{@{}lp{0.7\linewidth}@{}}
    437E & Biconical collet E20 with concentric clamping. Bore diameters from Ø 3 to 10 mm.                                                                                           \\
    1184 & Dial indicator with mounting bracket for depth measurement. 1 division = 0.0025 mm.                                                                                        \\
    235B & Boring chuck Ø 24 mm for bores from 2 to 40 mm. Cylindrical shank Ø 10 mm. Key, reduction sleeves, square, tool holder, high-speed steel tools, and shims in a wooden box. \\
\end{tabular}

\section*{Cleaning, Lubrication, and Maintenance}
Upon receipt and during use, follow the general guidelines provided for the machine. The quick head includes 2 oilers for pressurized lubrication using the pump supplied with the machine.

\section*{Installation}
The quick head is centered and secured by the two support arms 7. For installation, insert the gear rack 141 (supplied with the quick head and identical to that of the vertical head) into the spindle nose, then tighten it with the wrench. Extend one of the support arms 7 by about 250 mm and lock the front screw 5. Mount the quick head on the support arm in the corresponding bore of the quick head. This mounting method avoids jams that may occur when both support arms engage simultaneously. Then press the quick head against the face of the spindle head, taking care not to damage the gear teeth. Immobilize the support arms 7 with the two screws 5 and tighten the locking screw 80 by pressing the quick head firmly against the spindle head to prevent any torsion. Finally, tighten the 2 fixing screws 81.

\section*{Spindle}

The front bearing consists of a double-row ball bearing 120 (SKF 3205-C153) specially designed for high speeds. The rear bearing is a ball bearing 121 (SKF 6205-C153). If either of these bearings shows excessive wear, replace it as follows:
\vspace{-\parskip}
\begin{enumerate}
    \item To release the spiral spring 119, move the spindle to the upper position; unscrew the 4 fixing screws of the cover 118 and remove the control shaft complete with gear 123 and cover 118.
    \item Remove the cover 124 fixed by 2 screws.
    \item Unscrew the nut 126 locked by the lock washer 127 and remove the gear wheel 128.
    \item Loosen the screw 129 and remove the quill 130 from its housing.
    \item Unscrew the nut 131 locked by the lock washer 132.
    \item Disassemble the spindle 134 and replace the defective bearing.
\end{enumerate}
