\chapter{Automatic Slow-motion Vertical and Long Feeds}

The feedbox, independent of the spindle speeds, enables 8 feeds
(11 to 225 mm.) to be selected by operating lever 37 and turning
knob 36. The feeds are read off the graduated ring 38 mounted on
the knob 36. By means of a patented, automatic device the running
direction of the milling spindle can be reversed (e.g., for left-
hand cutters) without reversing the feed gear, thus proventing any
wrong manipulations.

Accidents due to unforeseen overloads are prevented by a friction
clutch. The drive is transmitted from the motor to the feed gear
through a vee-belt ansvewing to the following specification:

\begin{itemize}
    \item Profile: 10 x 6
    \item Angle: \(30^\circ\)
    \item Length: 750 mm
\end{itemize}

If it is desired, for instance, to set a feed of 29 mm./min.,
knob 36 must be turned until the figure 29 is on top. The colours
on the graduated ring 38, on which the number 29 is marked,
indicate whether the lever 37 must be pushed or pulled (for 29 mm./
min. green colour; pull lever 37). Whilst the motor is running,
these operations can be performed on the lower feed range only.

The feed set in mm./min. applies both to the vertical and to the
long feed.

The automatic feed is disengaged when lever 37 is in its middle
position.

The automatic movements of the table are controlled by shifting a
single lever, 39, in the direction of the desired feed. When this
lever is shifted to the right, the table feeds to the right; when
the lever is shifted upwards, the table moves upwards. With the
lever in its middle position, the table remains stationary.


\ul{The adjustable trip blocks 40 and 41} automatically stop the table
at the desired position. For stopping the long feed, the automatic
feed is first disengaged by a portion of the head of the set
screw 42, which presses against the roller 43. Feed is then conti-
nued by hand until the set-screw 42 brings up by another part of
its head against the fixed stop 44. In this way very accurate
stoppage of the table in the desired positions is achieved.
Never remove the end-stops 40 and 41.

    {\let\clearpage\relax


\chapter{Longitudinal and Vertical High-Speed Feed}}

The high-speed feed of 1000 mm./min. is independent of the slow-
motion feeds and is actuated by a separate motor housed in the
base. A slipping clutch is provided to prevent accidents and
overloading; adjustment is not necessary. The motor switch is
operated by pressing on the pedal 24 located on the front of
the base. By means of a patented device, the high-speed feed can
be engaged even when the table is already moving. This means
that the table can be fed forward at high speed until pressure
on the pedal 24 is removed, when the table will continue to
feed forward under the actuation of the slow-motion feed gear,
no manipulation of levers being required.
