\chapter{Service Instructions for Vise 35 For Use on Universal Milling Machine Schaublin 13 \small{Accessory No. 35}}

\section*{Main Features}


\begin{tabular}{@{}ll@{}}
    Jaw Width                        & 100 mm        \\
    Jaw Height                       & 30 mm         \\
    Maximum Opening                  & 70 mm         \\
    Total Height with Swivel Base    & 100 mm        \\
    Total Height without Swivel Base & 75 mm         \\
    Swiveling                        & \(360^\circ\)
\end{tabular}

\section*{Cleaning, Lubrication, and Maintenance}

Upon receipt and during operation, the provided instructions for the machine are valid and must be observed.
The vise includes an oiler for lubrication using a dropper.
By flipping the vise, the screw is accessible for periodic lubrication.

\section*{Usage}

The base is fixed on one of the T-slots of the table using two rods. Two locator blocks ensure alignment.

The vise is secured on the base in all positions by two rods.
Additionally, a central rod presses the base and vise onto the table.
Its effective tightening is at the tool contact point.

For simple tasks, the vise is used without the base.
The locator blocks of the base can be screwed onto the vise body in two positions: parallel or perpendicular to the jaws.
The vise is then fixed on one of the T-slots of the table using the two rods from the base and a shorter central rod,
supplied with this accessory. The effective tightening of the central rod should not be neglected.
