\chapter{Lubrication and Maintenance}

Before the Miller is started up, all its operative parts must be
thoroughly oiled. We recommend for this purpose an oil having the
following characteristics:-

\begin{center}
    VISCOSITY 4,5째E at 50째C
\end{center}

The viscosity of the oil in the two oil baths must not exceed
4,5째E at 50째C. The following is the correct procedure for filling
the oil baths: -

\section*{Gearbox Oil Bath}

Slacken screw 5 and remove clamping-piece 6. Pull one of the
surrpoting arms 7 rearwards until the passage between the arm
guide hole and the clamping hole is clear. Fill, through the
apertune thus provided, up to the mark on the oil level gauge 8.
Drain by removing screw 9. (See page 10, A, and page 21).

\section*{Feed box Oil Bath}

Unscrew oil-level indicator 10 and fill up until the gears dip
into the oil (test by turning the wheels). A quantity of 0,2
litre (about 1/3 pint) is sufficient. Drain by unscrewing screw
11. (See page 10, B).

\section*{Draining the oil baths}

Once a year, drain the two oil baths, swill them out with
paraffin, and refill.

\section*{Lubricating the Variator}

Remove the cover 12 and fill the small reservoir with oil.
Check oil level weekly.

\section*{Lubricating the motors}

The bearings of the main drive motor, the high-speed feed motor
and the coolant pump motor should be greased with ball-bearing
grease. The instructions enclosed herewith contain full particulars
as to maintenance and lubrication of the motors.

\section*{Pressure Lubrication}

The other parts of the machine are lubricated once a week by
injection oil with an oil gun. All lubricating points are
indicated on page 11. 4 to 5 shots of oil per nipple are
sufficient.

\underline{The feed box is to be lubricated 2 - 3 times a week through red oil nipple.}

\section*{Lubricating the Vertical Feed Spindle}

Raise the table to its top position. Lift the telescoping guard
tubes and oil the feed-spindle with a hand oilcan. This operation
should be performed once weekly.
