\chapter{Dividing Head \small{Accessory No. 17}}

\section*{Main Features}

\begin{tabular}{@{}ll@{}}
    Center height                        & 62 mm  \\
    Spindle with threaded nose for chuck & No. 21 \\
    Collet bore                          & W20    \\
    Solid center with tightening key     &        \\
    Bench profile base                   &
\end{tabular}

\section*{Accessories}
\begin{tabular}{@{}ll@{}}
    780  & Long support arm, length 375 mm                            \\
    781  & Long support arm, length 475 mm                            \\
    110  & Circular divider, 60 teeth                                 \\
    108  & Spring ratchet                                             \\
    82   & 4-disc hole divider device                                 \\
    83   & Vernier dividing device                                    \\
    9012 & Drive dog                                                  \\
    4    & Clamp Type W20 Collet, Max Bore 20 mm, Max Passage 14.5 mm \\
\end{tabular}

\section*{Cleaning, Lubrication, and Maintenance}
Upon receipt and during operation, follow the provided instructions for the machine, which are valid and must be observed.
The dividing head includes an oiler for pressure lubrication using the pump supplied with the machine.

\section*{Installation}
The dividing head and the tailstock are fixed using tie rods on the swivel base No. 50 with a bench profile of 102.
This base allows a center distance of 265 mm.
For between-center work on base No. 8001, use arms No. 780 or 781, providing center distances of 105 or 205 mm.

The spindle is locked using lever 100.

\section*{Compensation of Spindle Axial Play}
\begin{enumerate}
    \item Unlock screws 101.
    \item Screw nut 102 according to the amount of play to be compensated.
    \item Tighten firmly both screws 101.
\end{enumerate}

\section*{Vernier Disassembly}
\begin{enumerate}
    \item Unscrew screw 103.
    \item Remove the pinion 104, the sleeve 105 carrying the vernier 106.
\end{enumerate}

\section*{Disassembly of Hole Disks}
\begin{enumerate}
    \item Unscrew screw 107.
    \item Remove the crank 108, the washer 109, and the needles 110.
    \item Unscrew the 3 screws 111 and remove disk 112.
\end{enumerate}

To release the spindle from the worm, unlock screw 113 and turn support 114.
