\chapter{Structural Details and Controls}\label{chap:structural_characteristics_and_handling}

\section*{Spindle Head}

The spindle head can be moved axially on the head frame by means
of a handwheel 25, with vernier, accessible from all directions.
The screw spindle has a pitch of 4 mm. The vernier is graduated
in 2/100 mm. and can be set at zero. The milling spindle 26, of
hardened chrome-nickel steel, runs in high-precision ball bearings.
The spindle nose is of the following type: ASA B5 18-1943 N° 30
(dimensions see page 21).

For adjustment of spindle bearings, see page 20.
The front of the spindle head is machined and the two supporting
arms 7 enable the special attachments and the outside bracket
for guiding the long milling-cutter arbors to be mounted.

\section*{frame}

The powerfully-ribbed frame is cast integral with the base in
extremely hard alloy cast iron, and its lower part houses the
drive members for the milling spindle and the feed gear, as well
as the coolant tank.

The upper portion of the frame encloses the gearbox, in which
all the gears are made of hardened and ground chrome-nickel
șteel. In conjunction with the speed regulator, which is likewise
mounted in the frame, this gear provides the very wide range of
speeds of 56 to 2100 r.p.m.

\section*{Starting Up}

Switch 22, housed in a case on the right-hand side of the frame,
enables the milling spindle to be started up and reversed with.
the aid of the lever 15. This lever is locked by means of screw
14, so that the direction of rotation, once set, is maintained.
If this screw is fitted in the centre of one the milling cutters
sketched on the plate - the one corresponding to the cutter
fitted to the spindle - the desired direction on rotation is
automatically obtained.

When the machine is shut down for a protracted period, it is
advisable to switch off the motor by means of the contactor
indicated by a plate bearing the image of a milling cutter.
The high-speed feed motor is started up by means of the
pedal 24 and the push-button switch 23 located respectively in
front of and on the base.

The coolant pump motor is started up by the push-button 21 on
the contactor marked by a plate showing a cock.
